Predicting Conflict Escalation

### 2023-05-02 docs/hes_final/article.qmd
Swapped FFNN and Transformer Sections

Our second approach used a pair of transformer models to extract information directly from the GDELT embedding corpus.[@vaswani2017attention] Architecturally, both models are encoder-only transformers, but for simplicity, we will refer to the first of these models as “the encoder” and the second as the “classifier”.

    Spike -->|included during model training| Trans1
```

@@

Our third approach employed a feed forward neural network model. Uniform manifold approximation and projection (UMAP) was used to reduce dimensionality of GDELT article embeddings in a supervised manner [@sainburg2021parametric]. Our spike variable was used to condition the dimension reduction process of the training data to encourage separation of the variable classes in the reduced embedding space. The fit UMAP model, was applied to the validation and test data without supervision. These reduced, 128 dimension embeddings, along with country context indicators, were used as inputs to a feed forward neural network with a single hidden layer of 32 neurons. The model's 4577 parameters were trained for 3 epochs.

@@

## Results

>>>>

@@

Our second approach employed a feed forward neural network model. Uniform manifold approximation and projection (UMAP) was used to reduce dimensionality of GDELT article embeddings in a supervised manner [@sainburg2021parametric]. Our spike variable was used to condition the dimension reduction process of the training data to encourage separation of the variable classes in the reduced embedding space. The fit UMAP model, was applied to the validation and test data without supervision. These reduced, 128 dimension embeddings, along with country context indicators, were used as inputs to a feed forward neural network with a single hidden layer of 32 neurons. The model's 4577 parameters were trained for 3 epochs.

@@

Our third approach used a pair of transformer models to extract information directly from the GDELT embedding corpus.[@vaswani2017attention] Architecturally, both models are encoder-only transformers, but for simplicity, we will refer to the first of these models as “the encoder” and the second as the “classifier”.

    Spike -->|included during model training| Trans1
```
## Results
